EAST: \textit{de novo} {\underline E}xpression Fragment {\underline A}ssembly from {\underline S}panning {\underline T}rees

### 2011-06-21 peace/papers/EAST.bioinf/east.tex
Updating paper submission.

\begin{figure}
\centerline{\includegraphics[width=3in]{pics.d/overlap_alignment.pdf}}
\caption{(a) Two sequences potentially overlapping at the ends.  (b)
  The window of $s_2$ pairing with the right-most window of $s_1$ to
  minimize the $d^2$ score.  (c) An extension of the $s_2$ window to
  the end of the sequence, and the corresponding extension on $s_1$.
  (d) A global alignment of the overlapping areas determined from
  (c).}\label{fig:overlap}
\end{figure}

@@

\begin{figure*}[htb]
\centerline{\includegraphics[width=6in]{pics.d/ascore_sanger_norm.pdf}}
\caption{Average normalized a-score as a function of base error rate for
  simulated Sanger sequencing.  \east=blue, \capthree=Black,
  \tgicl=green. COMMENT: Need to change figure heading to Normalized a-score.}
\label{sangerAscore}
\end{figure*}

@@

\begin{figure*}[htb]
\includegraphics[width=6in]{pics.d/numContigs_sanger.pdf}
\includegraphics[width=6in]{pics.d/numSingle_sanger.pdf}
\caption{Number of contigs (normalized to the number of transcripts)
  and number of singletons as a function of base-call error
  rate for simulated Sanger sequencing.}
\label{contigsSanger}
\end{figure*}

@@

\begin{figure*}[htb]
\centerline{\includegraphics[width=5in]{pics.d/ascore_nxtgen.pdf}}
\caption{Comparative normalized a-scores for 454 and Illumina sequence
  output, using the \metasim default model at different levels
  of coverage.}
\label{nextgenAscore}
\end{figure*}

@@

\begin{figure*}[htb]
\centerline{\includegraphics[width=5in]{pics.d/ascore_hybrid.pdf}}
\caption{Comparative normalized a-scores for a hybrid set consisting
  of Sanger, 454 and Illumina sequence output, varying the base-call
  error rate for Sanger sequences and using the MetaSim default model
  for the 454 and Illumina sequences.  Each data set tested was
  composed of 40\% Sanger Sequences, 40\% 454 Sequences, and 20\%
  Illumina sequences.}
\label{hybridAscore}
\end{figure*}

@@

\begin{figure*}[htb]
\centerline{\includegraphics[width=6in]{pics.d/runtime_fixedsize_sanger.pdf}}
\caption{Average runtime per trial when generating data for
  Figures~\ref{sangerAscore}-\ref{hybridAscore}  when coverage = 30.
  Note that the exceptionally high speed of \velvet\/ on Illumina sequences make the
  red (center) bars in that plot essentially indistinguishable.}
\label{runtime.fixed}
\end{figure*}

\begin{figure*}[htb]
\centerline{\includegraphics[width=6in]{pics.d/runtime_bycoverage_all.pdf}}
\caption{The average runtime when applying each tool to a simulated
  data set derived from a specific zebrafish transcript of length
  14,625 bp.  As we decrease coverage the number of fragments drops,
  hence illustrating the relationship between tool runtime and
  fragment set size.  Each data point represents the average runtime
  from the application of the tool to at least 30 randomly generated
  simulated sets coming from the transcript at the given level of
  coverage.}
\label{runtime.coverage}
\end{figure*}

>>>>

\begin{figure}
\centerline{\includegraphics[width=3in]{overlap_alignment.pdf}}
\caption{(a) Two sequences potentially overlapping at the ends.  (b)
  The window of $s_2$ pairing with the right-most window of $s_1$ to
  minimize the $d^2$ score.  (c) An extension of the $s_2$ window to
  the end of the sequence, and the corresponding extension on $s_1$.
  (d) A global alignment of the overlapping areas determined from
  (c).}\label{fig:overlap}
\end{figure}

@@

\begin{figure*}[htb]
\centerline{\includegraphics[width=6in]{ascore_sanger_norm.pdf}}
\caption{Average normalized a-score as a function of base error rate for
  simulated Sanger sequencing.  \east=blue, \capthree=Black,
  \tgicl=green. COMMENT: Need to change figure heading to Normalized a-score.}
\label{sangerAscore}
\end{figure*}

@@

\begin{figure*}[htb]
\includegraphics[width=6in]{numContigs_sanger.pdf}
\includegraphics[width=6in]{numSingle_sanger.pdf}
\caption{Number of contigs (normalized to the number of transcripts)
  and number of singletons as a function of base-call error
  rate for simulated Sanger sequencing.}
\label{contigsSanger}
\end{figure*}

@@

\begin{figure*}[htb]
\centerline{\includegraphics[width=5in]{ascore_nxtgen.pdf}}
\caption{Comparative normalized a-scores for 454 and Illumina sequence
  output, using the \metasim default model at different levels
  of coverage.}
\label{nextgenAscore}
\end{figure*}

@@

\begin{figure*}[htb]
\centerline{\includegraphics[width=5in]{ascore_hybrid.pdf}}
\caption{Comparative normalized a-scores for a hybrid set consisting
  of Sanger, 454 and Illumina sequence output, varying the base-call
  error rate for Sanger sequences and using the MetaSim default model
  for the 454 and Illumina sequences.  Each data set tested was
  composed of 40\% Sanger Sequences, 40\% 454 Sequences, and 20\%
  Illumina sequences.}
\label{hybridAscore}
\end{figure*}

@@

\begin{figure*}[htb]
\centerline{\includegraphics[width=6in]{runtime_fixedsize_sanger.pdf}}
\caption{Average runtime per trial when generating data for
  Figures~\ref{sangerAscore}-\ref{hybridAscore}  when coverage = 30.
  Note that the exceptionally high speed of \velvet\/ on Illumina sequences make the
  red (center) bars in that plot essentially indistinguishable.}
\label{runtime.fixed}
\end{figure*}

\begin{figure*}[htb]
\centerline{\includegraphics[width=6in]{runtime_bycoverage_all.pdf}}
\caption{The average runtime when applying each tool to a simulated
  data set derived from a specific zebrafish transcript of length
  14,625 bp.  As we decrease coverage the number of fragments drops,
  hence illustrating the relationship between tool runtime and
  fragment set size.  Each data point represents the average runtime
  from the application of the tool to at least 30 randomly generated
  simulated sets coming from the transcript at the given level of
  coverage.}
\label{runtime.coverage}
\end{figure*}
